Controlled growth and property measurement of one-dimensional oxide nanostructures for energy applications

### 2015-03-29 ch-wox/part1.tex
Final

Besides \ce{WO3}, tungsten oxide exists in a series of sub-stoichiometric states. The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ \gls{cs} structure. Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=WO_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every $n$ row. Actually the value $x$ in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3. \ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure. Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$. For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where $x$ is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for $x$ within 2.87 to 2.93.\cite{Sloan1999} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm of \ce{WO3} layers. Localized surface plasmons could possibly exist on these conductive planes. Therefore \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.\cite{Shingaya2013}
% wo3 phases
\begin{table}[htb]
\centering
\caption{List of \ce{WO3} phases}\label{tab:wo3phase}
\begin{tabular}{lccccc}
\toprule
&&&\multicolumn{3}{c}{Lattice constants \AA} \\
\cmidrule(l){4-6}
 Symbol    & Temperature (\si{\degreeCelsius}) & Phase & a & b & c   \\
\midrule
$\epsilon$-\ce{WO3} & $ -140 \sim -50$  & monoclinic II & 7.378 & 7.378 & 7.664  \\
$\delta$-\ce{WO3} & $-50 \sim 17$  & triclinic & 7.309 & 7.522 & 7.686  \\
$\gamma$-\ce{WO3} & $17 \sim 330$  & monoclinic I & 7.306 & 7.540 & 7.692  \\
$\beta$-\ce{WO3} & $330 \sim 740$  & orthorhombic & 7.384 & 7.512 & 3.846  \\
$\alpha$-\ce{WO3} & $> 740$  & tetragonal & 5.25 & NA & 3.91  \\
$h$-\ce{WO3} &  $<400$  & hexagonal & 7.298 & NA & 3.899  \\
\bottomrule
\end{tabular}
\end{table}
Tungsten oxides were probably best known for the electrochromic effect, meaning the coloration (deep blue) and bleaching (transparent) states of \ce{WO3} are reversibly switched upon forward and backward voltage, and the coloration or bleached states remain after disconnecting the voltage. On basis of this property, \gls{ecd} of tremendous energy saving potential is conceptualized and some products have already been commercialized (i.e. smart window\footnote{"We did a case study in five cities, and the average savings in commercial buildings are about 25 percent of the heating, ventilation, and air-conditioning energy use annually," said CEO of View, Inc.}), although the materials used is not clear.

@@

Therefore another model in analogy to the F-color center is proposed. Color center model assumes the presence of oxygen vacancy $V_O^0$ is associated with \ce{W^{4+}} or 2\ce{W^{5+}} states. This defect level is expected to be inside or near the valence band. When one electron is removed from this level, $V_O^0$ is converted to $V_O^+$. The positively charged vacancy exerts Coulombic repulsion to the nearest W-ions, which results in a displacement of the neighboring W-ions and an upward shift of the defect level into the bandgap, thereby creating a color center. The optical transition from $V_O^+$ to $V_O^{2+}$ (a state within the conduction band) contributes to coloration.\cite{Deb2008}

So the polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration; but disagree on how this \ce{W^{5+}} state and the corresponding energy levels are created (foreign ion reduction in polaron model and oxygen vacancy in color center model). A modified polaron model is proposed to include \ce{W^{4+}} states in host lattice. Coloration mechanism is represented by Eq.~\ref{eq:cl_bl1} and \ref{eq:cl_bl2}, which described the polaron hopping from one site to another.\cite{Chatten2005}
\begin{align}
h\nu +\ce{W^{5+}(A)} +  \ce{W^{6+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{6+}(A) + E_{phonon}} \label{eq:cl_bl1}\\
h\nu +\ce{W^{5+}(A)} +  \ce{W^{4+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{4+}(A) + E_{phonon}} \label{eq:cl_bl2}
\end{align}
Similar scenario occurs in the gasochromic effect. Two models, double injection and color center, arise to account for the coloration upon exposure to certain gases. Both consent to Eq.~\ref{eq:cl_bl1}. But there is a disagreement on the final states. Double injection model supports the formation of tungsten bronze \ce{H_xWO3} while color center model insists on the inward diffusion of oxygen vacancy and outward diffusion of water molecules. Both have been substantiated experimentally;\cite{Zhu2010} therefore, the exact mechanism in \ce{WO_x} still requires further investigation.

>>>>

Besides \ce{WO3}, tungsten oxide exists in a series of sub-stoichiometric states. The \ce{W_nO_{3n-1}} ($n \geq 2$) exhibit $\{ 001 \}$ \gls{cs} structure. Chemical formula corresponding to n=2, 3, 4, 5 and 6 are \ce{W2O5=WO_{2.5}}, \ce{W3O8=WO_{2.67}}, \ce{W4O_{11}=WO_{2.75}}, \ce{W5O_{14}=WO_{2.8}}, and \ce{W6O_{17}=WO_{2.83}}, which indicates the existence of a oxygen deficient plane at every $n$ row. Actually the value $x$ in \ce{WO_x} could almost continuously vary within a range of 2.5 to 3. \ce{W_{18}O_{49}=\ce{WO_{2.72}}} is an exception without $\{ 001 \}$ CS structure. Moreover, the oxygen deficient planes could extend along directions other than $\{ 001 \}$. For instance, the $\{ 102 \}$ CS planes appears in \ce{WO_x} where $x$ is within 2.93 to 2.98, and  the $\{ 103 \}$ CS planes for $x$ within 2.87 to 2.93.\cite{Sloan1999} In \ce{WO_x} nanorods, the oxygen deficient planes are conductive, each having atomic thickness and separated by several nm of \ce{WO3} layers. Localized surface plasmons could possibly exist on these conductive planes. Therefore, \gls{sers} applies and single molecule Raman scattering using individual tungsten oxide nanorod has been demonstrated.\cite{Shingaya2013}
% wo3 phases
\begin{table}[htb]
\centering
\caption{List of \ce{WO3} phases}\label{tab:wo3phase}
\begin{tabular}{lccccc}
\toprule
&&&\multicolumn{3}{c}{Lattice constants \AA} \\
\cmidrule(l){4-6}
 Symbol    & Temperature (\si{\degreeCelsius}) & Phase & a & b & c   \\
\midrule
$\epsilon$-\ce{WO3} & $ -140 \sim -50$  & monoclinic II & 7.378 & 7.378 & 7.664  \\
$\delta$-\ce{WO3} & $-50 \sim 17$  & triclinic & 7.309 & 7.522 & 7.686  \\
$\gamma$-\ce{WO3} & $17 \sim 330$  & monoclinic I & 7.306 & 7.540 & 7.692  \\
$\beta$-\ce{WO3} & $330 \sim 740$  & orthorhombic & 7.384 & 7.512 & 3.846  \\
$\alpha$-\ce{WO3} & $> 740$  & tetragonal & 5.25 & NA & 3.91  \\
$h$-\ce{WO3} &  $<400$  & hexagonal & 7.298 & NA & 3.899  \\
\bottomrule
\end{tabular}
\end{table}
Tungsten oxides were probably best known for the electrochromic effect, meaning the coloration (deep blue) and bleaching (transparent) states of \ce{WO3} are reversibly switched upon forward and backward voltage, and the coloration or bleached states remain after disconnecting the voltage. On basis of this property, \gls{ecd} of tremendous energy saving potential is conceptualized and some products have already been commercialized (i.e. smart window\footnote{"We did a case study in five cities, and the average savings in commercial buildings are about 25 percent of the heating, ventilation, and air-conditioning energy use annually," said CEO of View, Inc.}), although the materials used is not clear.

@@

Therefore, another model in analogy to the F-color center was proposed. Color center model assumes the presence of oxygen vacancy $V_O^0$ is associated with \ce{W^{4+}} or 2\ce{W^{5+}} states. This defect level is expected to be inside or near the valence band. When one electron is removed from this level, $V_O^0$ is converted to $V_O^+$. The positively charged vacancy exerts Coulombic repulsion to the nearest W-ions, which results in a displacement of the neighboring W-ions and an upward shift of the defect level into the bandgap, thereby creating a color center. The optical transition from $V_O^+$ to $V_O^{2+}$ (a state within the conduction band) contributes to coloration.\cite{Deb2008}

The polaron and color center models both agree on that \ce{W^{5+}} and its transition is responsible for the coloration; but disagree on how this \ce{W^{5+}} state and the corresponding energy levels are created (foreign ion reduction in polaron model and oxygen vacancy in color center model). A modified polaron model is proposed to include \ce{W^{4+}} states in host lattice. Coloration mechanism is represented by Eq.~\ref{eq:cl_bl1} and \ref{eq:cl_bl2}, which described the polaron hopping from one site to another.\cite{Chatten2005}
\begin{align}
h\nu +\ce{W^{5+}(A)} +  \ce{W^{6+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{6+}(A) + E_{phonon}} \label{eq:cl_bl1}\\
h\nu +\ce{W^{5+}(A)} +  \ce{W^{4+}(B)} &\rightarrow \ce{W^{5+}(B)} + \ce{W^{4+}(A) + E_{phonon}} \label{eq:cl_bl2}
\end{align}
Similar scenario occurs in the gasochromic effect. Two models, double injection and color center, arise to account for the coloration upon exposure to certain gases. Both consent to Eq.~\ref{eq:cl_bl1}. But there is a disagreement on the final states. Double injection model supports the formation of tungsten bronze \ce{H_xWO3} while color center model insists on the inward diffusion of oxygen vacancy and outward diffusion of water molecules. Both have been substantiated experimentally;\cite{Zhu2010} therefore, the exact mechanism in \ce{WO_x} still requires further investigation.

### 2015-03-29 main.tex
Final

>>>>

Similar phenomena were observed in other studies. \citeauthor{Thangala2007} reported that a decrease in NW density with increasing substrate temperature, and an increase of NW density with increasing partial pressure of oxygen.\cite{Thangala2007}

When the catalyst was smaller than some critical size, there is no preferred growth direction. This changed when the precipitated solid exceeded certain critical dimension, and the morphology evolution was then determined by the relative size of already formed solid and the associated catalyst.

forming a swelling particle

 the tips of \ce{WO3} NWs exhibited greater crystalline disorder, and \ce{WS2} layers on tips were folded at least along two axes, resulting a higher density of defects and thus a higher sulfurization rate; while the folding along NW body was quasi-one dimensional, subsequently the sulfurization rate could be lower. Besides, sulfurization could also be initiated from the NW body, presumably due to the presence of surface defects. As a result, this led to the uneven \ce{WS2} layer number distribution along the core-shell NWs.

which was tentatively attributed to stacking fault in this study.

### 2015-03-29 misc/paper.tex
Final

\begin{table}[htb]
\centering
\caption{Materials in Si photonics}
\begin{tabular}{lcp{3in}r}
\toprule
Composition & Function &  Property & Ref   \\
\midrule
Si          &    &   direct gap 3.4 eV,     &    \\
Si          &  waveguide  &   $n=3.47$@1550 nm,     &    \\
Si          &  modulator  &  $\chi^{(2)}$ 122 pm/V  &    \\
\ce{LiNbO3} &  modulator  &  $\chi^{(2)}$ 360 pm/V  &    \\
InP         &  detector  &   footprint 50 $\mu m^2$, 33 GHz        &    \\
SiGe        &  detector    &  0.7 eV, up to 1.7 $\mu$m        &    \\
cobalt salicide  &     &         &    \\
\bottomrule
\end{tabular}
\end{table}

@@

@@

model also is applicable to ..., more probable,

@@

>>>>

taper design beam propagation method and FDTD,\cite{Almeida2003} mode field resides in the \ce{SiO2} cladding region,

Low temp. oxygen-plasma assisted wafer bonding for hybrid Si laser.\cite{Park2005} Process:
\begin{enumerate}
\item \ce{SiO2} mask layer formation on SOI by 2 h at 1050 C
\item Silicon rib waveguide by inductively coupled plasma etching with \ce{Cl2}/\ce{BCl3}
\item cleaning
\item oxygen-plasma assisted wafer bonding: annealing at 300 C, 1.5 MPa for 12 h
\item InP removal by HCl at 250 C
\item diced, polished, and coated with \ce{SiO2}/\ce{Ta2O5}
\item n-contact: Ni/AuGe/Ni/Au
\item p-contact: Pd/Ti/Pd/Au
\end{enumerate}

Electrically pumped hybrid Si laser.\cite{Fang2006} 0.5 mW fiber coupled power and 70 C operating temp. for commercial transmitters. yield dominated by waveguide chipping and bond delamination during facets polishing.

DFB Si laser.\cite{Fang2008}

\begin{enumerate}
\item grating formation: 50 nm PECVD \ce{SiO2} patterned with e-beam lithography and inductively coupled plasma dry etching; 
\item 
\end{enumerate}

Hybrid laser development history.\cite{Bowers2010} 650 C bonding led to cracks. 300 C plasma-activated approach with vertical outgassing channel. Cleaving yielded stepped facets due to incorrect orientation of silicon. current could not be passed through the bonded interface due to thin oxide layer formation increasing the junction resistance. DFB laser were important because they removed the need for polished facets and enable single wavelength operation capability that is needed in DWDM.

design principles:
\begin{enumerate}
\item taper angle small to prevent coupling from low order mode to high order ones.
\item 
\item 
\end{enumerate}

wg on SOI.\cite{Kurdi1988} high density of carriers reduces the refraction index. SOI formation: high dose of oxygen ions implantation ($10^{18}$ ions/cm2) on sub. held at a temp. range of 450 to 600 C; abbreviated as SIMOX. postannealing at a temperature $T>1250$ C, defect densities can be as low as $10^5$ cm-2 when SIMOX samples annealed at $T=1300$ C. The top layer Si thickness can be increased by a subsequent epitaxial growth. For 200 nm top Si, the loss of TE0 mode is 1 dB/cm when \ce{SiO2} thickness reached 500 nm. High order modes suffer orders of magnitude higher attenuation.

InP electrical conductivity tuning by proton bombardment.\cite{Boudinov2001} Carrier trap center creation and thermal activation.

Single-mode SOI wg.\cite{Vivien2002} birefringence either due to effective index difference or group index difference between TE and TM modes. $n_g = n_{eff} - \lambda \frac{\partial n_{eff}}{\partial\lambda}$.

Plasma-Assisted InP-Si bonding.\cite{Pasquariello2002} Gallium arsenide, indium phosphide. bonding thermally mismatched materials cause degradation. thermal stress. wafer bonding requires surface roughness below 1 nm. eutectic bonding as alternative, indium-gold eutectic bonding. use Pd to form an ohmic contact in between InP and Si or GaAs. Anodic bonding; Hydrophilic wafer bonding; Hydrophobic surface obtained on HF treated InP and Si, and HCl or \ce{NH4OH} treated GaAs. Fluorine may be still on the surfaces.

Plasma is a partially ionized gas with equal charges. Electron are more mobile, thus the plasma potential is always positive. An ion current formed between the plasma and the chamber wall. Oxygen plasma is attractive for surface pretreatment in wafer bonding since it is efficient in removing hydrocarbon and water related species.

Pressure of 0.25 MPa on 2 inch wafer, nearly 50 kg.

Short cavity length DFB laser on Si with high efficiency, direct modulation.\cite{Zhang2014d} First order grating on Si defined with e-beam lithography; transmission line measurement for n- and p-contact resistance. grating pitch. Low thermal conductivity of BOX layer. 12.5 GB/s with 3 dB eye diagram demonstrated.

A path to PIC. \cite{Bowers2014}
\begin{enumerate}
\item III-V chips bonded on Si.
\item epitaxial growth of III-V layers on Si using buffer layers (Ge or strained supperlattices); however, this dislocation filter layers are absorptive and thick, limiting the efficient coupling into Si wg.
\item a 
\end{enumerate}

\begin{table}[htb]
\centering
\caption{Materials in Si photonics}
\begin{tabular}{lcp{3in}r}
\toprule
Composition & Function &  Property & Ref   \\
\midrule
Si          &    &   direct gap 3.4 eV,     &    \\
Si          &  waveguide  &   $n=3.47$@1550 nm,     &    \\
Si          &  modulator  &  $\chi^{(2)}$ 122 pm/V  &    \\
\ce{LiNbO3} &  modulator  &  $\chi^{(2)}$ 360 pm/V  &    \\
InP         &  detector  &   footprint 50 $\mu m^2$, 33 GHz        &    \\
InP         & gain medium  &   thermal $4.8\times 10^{-6}$ K        &    \\
Si         &  sub  &   thermal $2.6\times 10^{-6}$ K        &    \\
SiGe        &  detector    &  0.7 eV, up to 1.7 $\mu$m        &    \\
cobalt salicide  &     &         &    \\
\bottomrule
\end{tabular}
\end{table}

@@

\subsection{EAM thesis}

Frequency chirping from directly modulated lasers, where the pulse becomes broadening after transmitting through a dispersive fiber. External modulation also show chirping, but at a much lower magnitude. Time division multiplexing: Optical TDM, mode-locking source, time delay, the return-to-zero signal requires double bandwidth than do the non-return-to-zero signal. Electrical TDM.

\begin{itemize}
\item Electro-optic effect: change of refraction index by E field
\item Electroabsorption: change of absorption in the presence of E field. Franz-Keldysh effect in bulk and quantum confined Stark effect in QW. 
\item FK effect: below-bandgap photon-assisted tunneling of electrons from VB to CB. In bulk materials with E field applied, exciton ionization occurs predominately.
\item QCSE: when E field applies, optical absorption redshift, and exciton remains due to the large binding energy in QW. 
\end{itemize}

Using traveling wave electrode configuration, the reflection at the load end is diminished significantly, thus bypassing the RC limitation. Increasing well thickness leads to stronger QCSE and a lower driving voltage. The QW has to be designed with an absorption edge just slightly shorter than operation wavelength, such as 1490 nm for 1550 operation; a closer wavelength causes higher residual absorption without bias, and a shorter wavelength requires larger bias voltage.

Heavy hole transitions related to absorption of TE; and light hole related to TM. 
Heavy- and light-hole degeneracy is sufficient to ensure the polarization insensitivity of absorption for MQW using QCSE. Photo-generated holes accumulated in the wells, screening the applied field.

Traveling wave electrode design: carrier sweep out time and optical-electrical group velocity mismatch.

Transmission line. three modes in microstrip: dielectric quasi-TEM mode, skin-effect mode and slow-wave mode.

mesa, epoxy,

ref 30

\begin{table}[htb]
\centering
\caption{Comparison of modulator}
\begin{tabular}{cccc}
\toprule
Material   & Voltage &  Bandwidth   & Remarks   \\
           & (V)     &  (GHz)      &    \\
\midrule
\ce{LiNbO3}&  3-5     &  40   &    EO MZ      \\
InP, MQW   &  2-4     &  10   &    EO MZ      \\
InGaAs   &  1.5-3     &  30   &    EAM        \\
\bottomrule
\end{tabular}
\end{table}

\section{edx nanoelectronics}

Previously, diffusive random walk; current flow in nanoscale: ballistic, resistance calculation depending on the device length vs. mean free path. resistance associated with voltage drop.

Entropy driven process and mechanics force driven;

\[
G = \frac{q^2}{h}M\times\frac{\lambda}{L+ \lambda} \text{Ballistic conductance}
\]

positive voltage lower the electrochemical potential by amount of $qV$. conductance occurs only near the Fermi level. Current flow driven by E field?

Ballistic: no lost of momentum. Elastic: no lost of energy?  
For low bias (small than kT), conductance approximately as
\[
G = \int_{-\infty}^{+\infty} dE -\frac{\partial f_0}{\partial E}G(E)
\]

@@

model also is applicable to ..., more probable, material degradation,

@@

You can't make a silk purse out of a sow's ear
